### 2021-01-28 paper.tex
Formal Specification

\subsection {Formal verification}
\section{Formal specification}
\subsection {The Model Checking Language}
\subsection {Construction of the formal specification of security guidelines in MCL}
\section{Program model Construction}
\subsection {Verification Framework}
\subsection {Related Work}
\section{Conclusion}
\end{document}

>>>>

\subsection{Construction of the Formal Specification of Security
Guidelines in Model Checking Language}
Having presented the formalism that we adopt to specify the security guidelines, we
examine its applicability on a number of guidelines that we have considered. Before
proceeding to the formal specification, we explain the methodology that we provide
to the security expert to build the MCL mathematical formulas from the guidelines
descriptions.
The formalization flow is the following:

– Extraction of the keywords (action patterns) and the key-concepts from the guide-
line textual description

– Construction of the basic MCL formula
– Construction of the MCL formula involving explicit and implicit dependencies
Each step as well as the transition from one step to another are depicted in detail in
the next sections.
The proposed formalization in the MCL language presents the key concepts required by
each of the guidelines. The challenge is to define those concepts and actions and have
a unified yet extensible set of keywords that can be used by the security expert(s) to
formalize the guidelines. We tried to reduce the expert intervention by introducing the
Security Knowledge Base (See Section 7.5) which is a central repository containing the
different labels used for composing the guidelines, together with their description and
semantic meaning.

\subsubsection{Extracting the Key-concepts}
First, Brian, the security expert, is faced with the guideline written in natural lan-
guage, and needs to identify the key elements at the heart of the guideline (sensitive

data, security mechanism, etc.) before proceeding to the specification. Brian refers
to the Security Knowledge Base (SKB) (see Section 7.5), and more specifically to the
security guideline patterns and the labels that are used to build the formulas; they
can be used to guide Brian when building the formulas based on the existing patterns.
This operation will result in a basic formula; the term basic means that the formula
involves the most intuitive and simplistic pattern that considers only the data assets

to be protected. The basic formula does not involve the explicit or the implicit de-
pendencies that data might have. For instance, if the data was assigned to a variable (implicitly or explicitly), this data dependency will not be captured in the basic formula.
Let us take a closer look at some of the guidelines that we have surveyed, and explain
how Brian proceeds to build them. We have considered the three guidelines IDS03-J:Do
not log unsanitized user input [30], MSC62-J:Store passwords using a hash
function [40] and OWASP: Store unencrypted keys away from the encrypted
data [119]. These three guidelines illustrate several concepts, such as the notion of
single or multiple parameters, patterns, etc.
Let us now look at the keywords and the concepts that Brian can extract from the textual
description, and provide explanation for each of them. It is important to mention the
following; considering only the textual title or the name of the guidelines is not sufficient,
we need also to look at the detailed textual explanations that provide very useful details,
such as the cryptographic algorithms that should be used, or the hashing method to be
applied in a reliable manner. For example, in the guideline MSC62-J:Store passwords
using a hash function [40], the hashing should be implemented through a robust
and reliable algorithm, and those details appear within the detailed description of the

guideline. CERT provides the following: Avoid defective functions such as the Message-
Digest Algorithm (MD5). Hash functions such as Secure Hash Algorithm (SHA)-1 and

SHA-2 are maintained by the National Security Agency and are currently considered
safe. However, SHA-1 is no longer a reliable hashing algorithm, it got recently broken
1 2
From this perspective, if we consider that any password hashing operation as safe, even
using a non-reliable algorithm, then this might lead to a violation of the password’s
integrity. This brought further reflection on the dictionary enrichment considering a
multitude of elements such as: the hashing/encryption algorithm to use in what context,
the key length, etc. To give another example, the usage of DES for symmetric encryption
purposes in indicated in our SKB as prohibited, as well as the hashing through MD5.

\subsubsection{Building the Basic Formulas}
Once the key-concepts are retrieved from the guideline textual description, Brian might
refer to the Security Knowledge Base to check whether the extracted words have a
matching entry. He might for instance find synonyms or semantically equivalent words
(labels) that can use to build the formula. Having selected the key concepts, Brian
proceeds to building the more natural and intuitive MCL formula.
Since establishing a single dictionary is the key to building the formulas, we identified
the need to have a central repository containing the guidelines relevant details, such
as the patterns and the labels used to build the guidelines formulas. Brian can access
this central repository (Security Knowledge Base 7.5) and can use it as a reference model. When formalizing the guidelines, Brian extracts the key concepts from the
textual description, and at this level, he consults the dictionary to see if the identified
concepts have already been used in other guidelines patterns, and to check if there exists
a pattern that he can make use of to build the formula. If not, Brian introduces the
new labels, and attributes semantics reflecting the meaning of those new labels. We
need to stress that our central repository (Security Knowledge Base in section 7.5) can
be extended to cover a wide range of security concepts.

\subsubsection{Patterns for the Formal Specification of Security Guidelines}
When formalizing the security guidelines described in the previous section, we have
noticed that there are recurring patterns. For instance, the notion of precedence arises
in different guidelines, and constrains the order of actions.
Since we aim at leveraging the workload and bringing assistance and guidance to the se-
curity expert, we decided to further simplify the formalization of the security guidelines

and propose property patterns. Thanks to these, the security expert will hopefully not
need to have full knowledge about the formal language expressiveness nor to master its
idioms. He would eventually prefer to have more guidance on how to use the language
features. This would improve the transformation of the security guidelines from natural
language to formulas.
Similarly to Dywer’s work \cite{Dwyer::1999}, we propose a catalog of patterns for security guidelines.

These patterns identified in [103] will allow programmers who are not necessarily ex-
perts in formal language to read a formal specification. As proposed in [103], we encode

guidelines as a collection of property patterns intended to simplify the specification ac-
tivity. These patterns belong to particular classes: Absence, Existence, and Universality

and occur in various scopes: Before, After, and Between. Those classes reflect specific
requirements such as the absence of an action, precedence of actions, response of an
action that is triggered by another action, etc. The proposed patterns were adopted by
the Bandera Specification Language \cite{corbett2002expressing}.

\subsection {Formal verification}
\section{Formal specification}
\subsection {The Model Checking Language}
\subsection {Construction of the formal specification of security guidelines in MCL}
\section{Program model Construction}
\subsection {Verification Framework}
\subsection {Related Work}
\section{Conclusion}

%% The Bibliography
%% ==> You need a file 'literature.bib' for this.
%% ==> You need to run BibTeX for this (Project | Properties... | Uses BibTeX)
\addcontentsline{toc}{chapter}{Bibliography} %'Bibliography' into toc
%\nocite{*} %Even non-cited BibTeX-Entries will be shown.
\bibliographystyle{plain} %Style of Bibliography: plain / apalike / amsalpha / ...
\bibliography{literature} %You need a file 'literature.bib' for this.
\end{document}
